---
title: "Seurat project"
output: word_document
---



```{r, warning=FALSE, message=FALSE, eval=FALSE}
install.packages("BiocManager")
library("BiocManager")
BiocManager::install("celldex")
install.packages("devtools")
library("celldex")
library("devtools")
install.packages("remotes")
library("remotes")
install.packages("rtools")
Sys.which("make")
install.packages("ggrepel")
library("ggrepel")
remotes::install_version("SeuratObject", "4.1.4", repos = c("https://satijalab.r-universe.dev", getOption("repos")))
remotes::install_version("Seurat", "4.4.0", repos = c("https://satijalab.r-universe.dev", getOption("repos")))
install.packages("dplyr")
install.packages("patchwork")
BiocManager::install("harmony")
BiocManager::install("SingleR")
BiocManager::install("SingleCellExperiment")
install.packages("SignacX")
BiocManager::install('EnhancedVolcano')
BiocManager::install("clusterProfiler")
BiocManager::install("org.Hs.eg.db")
BiocManager::install("edgeR")
devtools::install_github("jokergoo/ComplexHeatmap")
library("ComplexHeatmap")
library("circlize")
install.packages("Matrix")
library("Matrix")
set.seed(42)
```


```{r, warning=FALSE, message=FALSE, eval=FALSE}
library("BiocManager")
library("celldex")
library("devtools")
library("remotes")
library("ggrepel")
library("SeuratObject")
library("Seurat")
library("dplyr")
library("patchwork")
library("harmony")
library("ggplot2")
library("SingleR")
library("SingleCellExperiment")
library("SignacX")
library("EnhancedVolcano")
library("clusterProfiler")
library("enrichplot")
library("org.Hs.eg.db")
library("edgeR")
library("ComplexHeatmap")
library("circlize")
library("CellChat")
set.seed(42)
```



```

#Import data

```{r, warning=FALSE, message=FALSE, eval=FALSE}
Ctrl1_data <- Read10X("C:\\Users\\User\\OneDrive\\Desktop\\交大專題\\實作\\Ctrl\\Ctrl1")
Ctrl2_data <- Read10X("C:\\Users\\User\\OneDrive\\Desktop\\交大專題\\實作\\Ctrl\\Ctrl2")
Ctrl3_data <- Read10X("C:\\Users\\User\\OneDrive\\Desktop\\交大專題\\實作\\Ctrl\\Ctrl3")
Pat1_pre_data <- Read10X("C:\\Users\\User\\OneDrive\\Desktop\\交大專題\\實作\\patient\\pat1_pre")
Pat2_pre_data <- Read10X("C:\\Users\\User\\OneDrive\\Desktop\\交大專題\\實作\\patient\\pat2_pre")
Pat3_pre_data <- Read10X("C:\\Users\\User\\OneDrive\\Desktop\\交大專題\\實作\\patient\\pat3_pre")
Pat1_post_data <- Read10X("C:\\Users\\User\\OneDrive\\Desktop\\交大專題\\實作\\patient\\pat1_post")
Pat2_post_data <- Read10X("C:\\Users\\User\\OneDrive\\Desktop\\交大專題\\實作\\patient\\pat2_post")
Pat3_post_data <- Read10X("C:\\Users\\User\\OneDrive\\Desktop\\交大專題\\實作\\patient\\pat3_post")

Ctrl1 <- CreateSeuratObject(counts = Ctrl1_data, project = "project_12thschool", min.cells = 3, min.features = 200)
Ctrl2 <- CreateSeuratObject(counts = Ctrl2_data, project = "project_12thschool", min.cells = 3, min.features = 200)
Ctrl3 <- CreateSeuratObject(counts = Ctrl3_data, project = "project_12thschool", min.cells = 3, min.features = 200)
Pat1_pre <- CreateSeuratObject(counts = Pat1_pre_data, project = "project_12thschool", min.cells = 3, min.features = 200)
Pat2_pre <- CreateSeuratObject(counts = Pat2_pre_data, project = "project_12thschool", min.cells = 3, min.features = 200)
Pat3_pre <- CreateSeuratObject(counts = Pat3_pre_data, project = "project_12thschool", min.cells = 3, min.features = 200)
Pat1_post <- CreateSeuratObject(counts = Pat1_post_data, project = "project_12thschool", min.cells = 3, min.features = 200)
Pat2_post <- CreateSeuratObject(counts = Pat2_post_data, project = "project_12thschool", min.cells = 3, min.features = 200)
Pat3_post <- CreateSeuratObject(counts = Pat3_post_data, project = "project_12thschool", min.cells = 3, min.features = 200)

```
##存東西
```{r, warning=FALSE, message=FALSE, eval=FALSE}
setwd("C:\\Users\\User\\OneDrive\\Desktop\\交大專題\\實作\\RDS") #設置儲存資料夾路徑
getwd() #得知儲存資料夾路徑
saveRDS(Ctrl1, file = "Ctrl1.rds") #儲存Seurat格式
Ctrl1_1 <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/Ctrl1.rds") #讀檔案

saveRDS(Ctrl1, file = "Ctrl1.rds")
saveRDS(Ctrl2, file = "Ctrl2.rds")
saveRDS(Ctrl3, file = "Ctrl3.rds")
saveRDS(Pat1_pre, file = "Pat1_pre.rds")
saveRDS(Pat2_pre, file = "Pat2_pre.rds")
saveRDS(Pat3_pre, file = "Pat3_pre.rds")
saveRDS(Pat1_post, file = "Pat1_post.rds")
saveRDS(Pat2_post, file = "Pat2_post.rds")
saveRDS(Pat3_post, file = "Pat3_post.rds")
saveRDS(public_data_all, file = "public_data_all.rds")

Ctrl1 <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/Ctrl1.rds")
Ctrl2 <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/Ctrl2.rds")
Ctrl3 <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/Ctrl3.rds")
Pat1_pre <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/Pat1_pre.rds")
Pat2_pre <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/Pat2_pre.rds")
Pat3_pre <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/Pat3_pre.rds")
Pat1_post <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/Pat1_post.rds")
Pat2_post <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/Pat2_post.rds")
Pat3_post <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/Pat3_post.rds")
public_data_all <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/public_data_all.rds")
```

#QC
```{r, warning=FALSE, message=FALSE, eval=FALSE}
Ctrl1[["percent.mt"]] <- PercentageFeatureSet(Ctrl1, pattern = "^MT-")
Ctrl2[["percent.mt"]] <- PercentageFeatureSet(Ctrl2, pattern = "^MT-")
Ctrl3[["percent.mt"]] <- PercentageFeatureSet(Ctrl3, pattern = "^MT-")
Pat1_pre[["percent.mt"]] <- PercentageFeatureSet(Pat1_pre, pattern = "^MT-")
Pat2_pre[["percent.mt"]] <- PercentageFeatureSet(Pat2_pre, pattern = "^MT-")
Pat3_pre[["percent.mt"]] <- PercentageFeatureSet(Pat3_pre, pattern = "^MT-")
Pat1_post[["percent.mt"]] <- PercentageFeatureSet(Pat1_post, pattern = "^MT-")
Pat2_post[["percent.mt"]] <- PercentageFeatureSet(Pat2_post, pattern = "^MT-")
Pat3_post[["percent.mt"]] <- PercentageFeatureSet(Pat3_post, pattern = "^MT-")

VlnPlot(Ctrl1, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
VlnPlot(Ctrl2, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
VlnPlot(Ctrl3, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
VlnPlot(Pat1_pre, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
VlnPlot(Pat2_pre, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
VlnPlot(Pat3_pre, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
VlnPlot(Pat1_post, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
VlnPlot(Pat2_post, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
VlnPlot(Pat3_post, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)

```


#Visulization nCountRNA
```{r, warning=FALSE, message=FALSE, eval=FALSE}
Ctrl1@meta.data %>% 
  ggplot(aes(color=Ctrl1$orig.ident, x=Ctrl1$nCount_RNA, fill= Ctrl1$orig.ident)) + 
  geom_density(alpha = 0.2) + 
  scale_x_log10() + 
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = 900)
  
Ctrl2@meta.data %>% 
  ggplot(aes(color=Ctrl2$orig.ident, x=Ctrl2$nCount_RNA, fill= Ctrl2$orig.ident)) + 
  geom_density(alpha = 0.2) + 
  scale_x_log10() + 
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = 900)

Ctrl3@meta.data %>% 
  ggplot(aes(color=Ctrl3$orig.ident, x=Ctrl3$nCount_RNA, fill= Ctrl3$orig.ident)) + 
  geom_density(alpha = 0.2) + 
  scale_x_log10() + 
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = 500)

Pat1_pre@meta.data %>% 
  ggplot(aes(color=Pat1_pre$orig.ident, x=Pat1_pre$nCount_RNA, fill= Pat1_pre$orig.ident)) + 
  geom_density(alpha = 0.2) + 
  scale_x_log10() + 
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = 400)
  
Pat2_pre@meta.data %>% 
  ggplot(aes(color=Pat2_pre$orig.ident, x=Pat2_pre$nCount_RNA, fill= Pat2_pre$orig.ident)) + 
  geom_density(alpha = 0.2) + 
  scale_x_log10() + 
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = 1000)
  
Pat3_pre@meta.data %>% 
  ggplot(aes(color=Pat3_pre$orig.ident, x=Pat3_pre$nCount_RNA, fill= Pat3_pre$orig.ident)) + 
  geom_density(alpha = 0.2) + 
  scale_x_log10() + 
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = 500)
  
Pat1_post@meta.data %>% 
  ggplot(aes(color=Pat1_post$orig.ident, x=Pat1_post$nCount_RNA, fill= Pat1_post$orig.ident)) + 
  geom_density(alpha = 0.2) + 
  scale_x_log10() + 
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = 1100)

Pat2_post@meta.data %>% 
  ggplot(aes(color=Pat2_post$orig.ident, x=Pat2_post$nCount_RNA, fill= Pat2_post$orig.ident)) + 
  geom_density(alpha = 0.2) + 
  scale_x_log10() + 
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = 950)

Pat3_post@meta.data %>% 
  ggplot(aes(color=Pat3_post$orig.ident, x=Pat3_post$nCount_RNA, fill= Pat3_post$orig.ident)) + 
  geom_density(alpha = 0.2) + 
  scale_x_log10() + 
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = 1800)

```

#Visulization nFeatureRNA
```{r, warning=FALSE, message=FALSE, eval=FALSE}

Ctrl1@meta.data %>%
  ggplot(aes(color = Ctrl1$orig.ident, x = Ctrl1$nFeature_RNA, fill = Ctrl1$orig.ident)) +
  geom_density(alpha = 0.2) +
  scale_x_log10() +
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = c(600, 3500))
  
Ctrl2@meta.data %>%
  ggplot(aes(color = Ctrl2$orig.ident, x = Ctrl2$nFeature_RNA, fill = Ctrl2$orig.ident)) +
  geom_density(alpha = 0.2) +
  scale_x_log10() +
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = c(600, 3000))

Ctrl3@meta.data %>%
  ggplot(aes(color = Ctrl3$orig.ident, x = Ctrl3$nFeature_RNA, fill = Ctrl3$orig.ident)) +
  geom_density(alpha = 0.2) +
  scale_x_log10() +
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = c(330, 2800))

Pat1_pre@meta.data %>%
  ggplot(aes(color = Pat1_pre$orig.ident, x = Pat1_pre$nFeature_RNA, fill = Pat1_pre$orig.ident)) +
  geom_density(alpha = 0.2) +
  scale_x_log10() +
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = c(330, 3100))

Pat2_pre@meta.data %>%
  ggplot(aes(color = Pat2_pre$orig.ident, x = Pat2_pre$nFeature_RNA, fill = Pat2_pre$orig.ident)) +
  geom_density(alpha = 0.2) +
  scale_x_log10() +
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = c(700, 3500))
  
Pat3_pre@meta.data %>%
  ggplot(aes(color = Pat3_pre$orig.ident, x = Pat3_pre$nFeature_RNA, fill = Pat3_pre$orig.ident)) +
  geom_density(alpha = 0.2) +
  scale_x_log10() +
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = c(350, 2400))

Pat1_post@meta.data %>%
  ggplot(aes(color = Pat1_post$orig.ident, x = Pat1_post$nFeature_RNA, fill = Pat1_post$orig.ident)) +
  geom_density(alpha = 0.2) +
  scale_x_log10() +
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = c(600, 3600))


Pat2_post@meta.data %>%
  ggplot(aes(color = Pat2_post$orig.ident, x = Pat2_post$nFeature_RNA, fill = Pat2_post$orig.ident)) +
  geom_density(alpha = 0.2) +
  scale_x_log10() +
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = c(650, 3600))
  
Pat3_post@meta.data %>%
  ggplot(aes(color = Pat3_post$orig.ident, x = Pat3_post$nFeature_RNA, fill = Pat3_post$orig.ident)) +
  geom_density(alpha = 0.2) +
  scale_x_log10() +
  theme_classic() +
  ylab("Cell density") +
  geom_vline(xintercept = c(1000, 3800))
```


#Filtered
```{r, warning=FALSE, message=FALSE, eval=FALSE}
Ctrl1 <- subset(Ctrl1, subset = nCount_RNA >= 900 & nFeature_RNA >= 600 & nFeature_RNA <= 3500 & percent.mt < 20)
Ctrl2 <- subset(Ctrl2, subset = nCount_RNA >= 900 & nFeature_RNA >= 600 & nFeature_RNA <= 3000 & percent.mt < 20)
Ctrl3 <- subset(Ctrl3, subset = nCount_RNA >= 500 & nFeature_RNA >= 280 & nFeature_RNA <= 3300 & percent.mt < 20)
Pat1_pre <- subset(Pat1_pre, subset = nCount_RNA >= 400 & nFeature_RNA >= 300 & nFeature_RNA <= 3100 & percent.mt < 20)
Pat2_pre <- subset(Pat2_pre, subset = nCount_RNA >= 950 & nFeature_RNA >= 700 & nFeature_RNA <= 3500 & percent.mt < 20)
Pat3_pre <- subset(Pat3_pre, subset = nCount_RNA >= 500 & nFeature_RNA >= 350 & nFeature_RNA <= 2400 & percent.mt < 20)
Pat1_post <- subset(Pat1_post, subset = nCount_RNA >= 1100 & nFeature_RNA >= 600 & nFeature_RNA <= 3600 & percent.mt < 20)
Pat2_post <- subset(Pat2_post, subset = nCount_RNA >= 950 & nFeature_RNA >= 650 & nFeature_RNA <= 3600 & percent.mt < 20)
Pat3_post <- subset(Pat3_post, subset = nCount_RNA >= 1800 & nFeature_RNA >= 1000 & nFeature_RNA <= 3800 & percent.mt < 20)


Ctrl1 <- AddMetaData(Ctrl1, metadata = "Heathy_control", col.name = "Condition")
Ctrl2 <- AddMetaData(Ctrl2, metadata = "Heathy_control", col.name = "Condition")
Ctrl3 <- AddMetaData(Ctrl3, metadata = "Heathy_control", col.name = "Condition")
Pat1_pre <- AddMetaData(Pat1_pre, metadata = "Patient_pre_treatment", col.name = "Condition")
Pat2_pre <- AddMetaData(Pat2_pre, metadata = "Patient_pre_treatment", col.name = "Condition")
Pat3_pre <- AddMetaData(Pat3_pre, metadata = "Patient_pre_treatment", col.name = "Condition")
Pat1_post <- AddMetaData(Pat1_post, metadata = "Patient_post_treatment", col.name = "Condition")
Pat2_post <- AddMetaData(Pat2_post, metadata = "Patient_post_treatment", col.name = "Condition")
Pat3_post <- AddMetaData(Pat3_post, metadata = "Patient_post_treatment", col.name = "Condition")

```


#merge 單純合併
```{r, warning=FALSE, message=FALSE, eval=FALSE}
public_data_1 <- merge(Ctrl1, Ctrl2)
public_data_2 <- merge(public_data_1, Ctrl3)
public_data_3 <- merge(public_data_2, Pat1_pre)
public_data_4 <- merge(public_data_3, Pat2_pre)
public_data_5 <- merge(public_data_4, Pat3_pre)
public_data_6 <- merge(public_data_5, Pat1_post)
public_data_7 <- merge(public_data_6, Pat2_post)
public_data_all <- merge(public_data_7, Pat3_post)
merge(x=d1, y=list(d2, d3, d4)) #合併多個檔案
DefaultAssay(public_data_all) <- "RNA"


```

#integrated 耗CPU
```{r, warning=FALSE, eval=FALSE}
cell.list <- list(NC1, GDM1)

for (i in 1:length(cell.list)) {
  cell.list[[i]] <- NormalizeData(cell.list[[i]], verbose = FALSE)
  cell.list[[i]] <- FindVariableFeatures(
    cell.list[[i]], 
    selection.method = "vst", 
    nfeatures = 2000, 
    verbose = FALSE
  )
}

features <- SelectIntegrationFeatures(object.list = cell.list)

cell.list.anchors <- FindIntegrationAnchors(
  object.list = cell.list,
  anchor.features = features,
  dims = 1:20
)

publicdata <- IntegrateData(
  anchorset = cell.list.anchors,
  dims = 1:20
)
DefaultAssay(publicdata) <- "RNA"
```



### data process

#### normalize data

```{r, warning=FALSE, message=FALSE, eval=FALSE}
DefaultAssay(public_data_all) <- "RNA"
public_data_all <- NormalizeData(public_data_all)
```

####find variable feature

```{r, warning=FALSE, eval=FALSE}
public_data_all <- FindVariableFeatures(public_data_all, selection.method = "vst", nfeatures = 2000)
VariableFeaturePlot(public_data_all)
```

####scale data

```{r, warning=FALSE, eval=FALSE}
public_data_all <- ScaleData(public_data_all, features = VariableFeatures(object = public_data_all))
```
-----3/13做到這

####RunPCA

```{r, warning=FALSE, eval=FALSE}
public_data_all <- RunPCA(public_data_all, features = VariableFeatures(object = public_data_all))
ElbowPlot(public_data_all, ndims = 50) #取彎點以前的一個值
VizDimLoadings(public_data_all, dims = 1:9, nfeatures = 15)
```

####harmony 

merge data --> harmony: Batch effect correction.

```{r, warning=FALSE, eval=FALSE}
BiocManager::install("harmony")
library(harmony)
public_data_all <- harmony::RunHarmony(public_data_all,
                            group.by.vars = 'Condition',
                            reduction.save = 'harmony')
```

umap after harmony

```{r, warning=FALSE, message=FALSE, eval=FALSE}
public_data_all <- RunUMAP(public_data_all,
                 dims = 1:9,  #取到的彎點
                 reduction = "harmony",
                 reduction.name = 'harmonyumap')
DimPlot(public_data_all, group.by = 'Condition',reduction = 'harmonyumap') + labs(title = "UMAP")
```
---3/14進度
tSNE after harmony 耗時耗CPU

```{r, warning=FALSE, eval=FALSE}
public_data_all <- RunTSNE(public_data_all,
                 dims = 1:9,
                 reduction = "harmony",
                 reduction.name = "harmonytsne")
DimPlot(public_data_all, group.by = "Condition", reduction = "harmonytsne") + labs(title = "tSNE")
```


### cluster analysis

```{r, warning=FALSE, eval=FALSE}
names(public_data_all@reductions)
public_data_all <- FindNeighbors(public_data_all, reduction = "harmony", dims = 1:9) 
names(public_data_all@graphs)
public_data_all <- FindClusters(public_data_all, resolution = 0.1)
DimPlot(public_data_all, group.by = 'RNA_snn_res.0.1', reduction = 'harmonyumap', label = TRUE) + labs(title = "clustering")

```

---3/15


singleR

```{r, eval=FALSE}
ref <- celldex::DatabaseImmuneCellExpressionData()

results <- SingleR(test = as.SingleCellExperiment(public_data_all),
                   ref = ref, labels = ref$label.main)

results_fine <- SingleR(test = as.SingleCellExperiment(public_data_all),
                        ref = ref ,labels = ref$label.fine)

public_data_all$singleR_labels_m <- results$labels
public_data_all$singler_labels_fine <- results_fine$labels

DimPlot(public_data_all, reduction = 'harmonyumap', group.by = 'singleR_labels_m')
DimPlot(public_data_all, reduction = 'harmonyumap', group.by = 'singler_labels_fine')

table(public_data_all@meta.data$singleR_labels_m)
```


---3/16


### DEGs(differentially expressed genes) analysis
#DEG pre/post/HC
```{r, warning=FALSE, message=FALSE, eval=FALSE}
levels(public_data_all)
Idents(public_data_all) <- 'Condition'
DEG_patpre_HC <- FindMarkers(public_data_all, 
                   ident.1 = 'Patient_pre_treatment',
                   ident.2 = 'Heathy_control',
                   logfc.threshold = 0.25)
                   
DEG_patpre_HC$gene <- rownames(DEG_patpre_HC)
DEG_patpre_HC$significance <- DEG_patpre_HC$p_val_adj < 0.05 & abs(DEG_patpre_HC$avg_log2FC) > 0.5
DEG_patpre_HC <- DEG_patpre_HC %>% filter(p_val_adj < 0.05)
saveRDS(DEG_patpre_HC, file = "DEG_patpre_HC.rds")
DEG_patpre_HC <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/DEG_patpre_HC.rds")
                   
DEG_patpost_HC <- FindMarkers(public_data_all, 
                   ident.1 = 'Patient_post_treatment',
                   ident.2 = 'Heathy_control',
                   logfc.threshold = 0.25)
                   
DEG_patpost_HC$gene <- rownames(DEG_patpost_HC)
DEG_patpost_HC$significance <- DEG_patpost_HC$p_val_adj < 0.05 & abs(DEG_patpost_HC$avg_log2FC) > 0.5
DEG_patpost_HC <- DEG_patpost_HC %>% filter(p_val_adj < 0.05)
saveRDS(DEG_patpost_HC, file = "DEG_patpost_HC.rds")
DEG_patpost_HC <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/DEG_patpost_HC.rds")

DEG_patpre_patpost <- FindMarkers(public_data_all, 
                   ident.1 = 'Patient_pre_treatment',
                   ident.2 = 'Patient_post_treatment',
                   logfc.threshold = 0.25)
                   
DEG_patpre_patpost$gene <- rownames(DEG_patpre_patpost)
DEG_patpre_patpost$significance <- DEG_patpre_patpost$p_val_adj < 0.05 & abs(DEG_patpre_patpost$avg_log2FC) > 0.5
DEG_patpre_patpost <- DEG_patpre_patpost %>% filter(p_val_adj < 0.05)
saveRDS(DEG_patpre_patpost, file = "DEG_patpre_patpost.rds")
DEG_patpre_patpost <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/DEG_patpre_patpost.rds")

setwd("C:\\Users\\User\\OneDrive\\Desktop\\交大專題\\實作\\RDS") #設置儲存資料夾路徑
getwd() #得知儲存資料夾路徑

```
```
volcano plot

```{r, warning=FALSE, message=FALSE, fig.width=15, fig.height=12, eval=FALSE}
library(EnhancedVolcano)
EnhancedVolcano(DEG_patpre_HC,
                lab = rownames(DEG_patpre_HC),
                x = "avg_log2FC",
                y = "p_val_adj")
EnhancedVolcano(DEG_patpost_HC,
                lab = rownames(DEG_patpost_HC),
                x = "avg_log2FC",
                y = "p_val_adj")
EnhancedVolcano(DEG_patpre_patpost,
                lab = rownames(DEG_patpre_patpost),
                x = "avg_log2FC",
                y = "p_val_adj")
```

```

#DEG cells
```{r, warning=FALSE, message=FALSE, eval=FALSE}

levels(public_data_all)      
Idents(public_data_all) <- 'singleR_labels_m'

B_cells <- subset(public_data_all, idents = 'B cells')
T_cells_CD4 <- subset(public_data_all, idents = 'T cells, CD4+')
T_cells_CD8 <- subset(public_data_all, idents = 'T cells, CD8+')
Monocytes <- subset(public_data_all, idents = 'Monocytes')
NK_cells <- subset(public_data_all, idents = 'NK cells')



saveRDS(B_cells, file = "B_cells.rds")
saveRDS(T_cells_CD4, file = "T_cells_CD4.rds")
saveRDS(T_cells_CD8, file = "T_cells_CD8.rds")
saveRDS(Monocytes, file = "Monocytes.rds")
saveRDS(NK_cells, file = "NK_cells.rds")

B_cells <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/B_cells.rds")
T_cells_CD4 <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/T_cells_CD4.rds")
T_cells_CD8 <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/T_cells_CD8.rds")
Monocytes <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/Monocytes.rds")
NK_cells <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/NK_cells.rds")




Idents(T_cells_CD4) <- 'Condition'
levels(T_cells_CD4)
DEG_T4_pre_HC <- FindMarkers(T_cells_CD4, 
                   ident.1 = 'Patient_pre_treatment',
                   ident.2 = 'Heathy_control',
                   logfc.threshold = 0.25)
DEG_T4_pre_HC$gene <- rownames(DEG_T4_pre_HC)
DEG_T4_pre_HC$significance <- DEG_T4_pre_HC$p_val_adj < 0.05 & abs(DEG_T4_pre_HC$avg_log2FC) > 0.5
DEG_T4_pre_HC <- DEG_T4_pre_HC %>% filter(p_val_adj < 0.05)
saveRDS(DEG_T4_pre_HC, file = "DEG_T4_pre_HC.rds")
DEG_T4_pre_HC <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/DEG_T4_pre_HC.rds")

DEG_T4_post_HC <- FindMarkers(T_cells_CD4, 
                   ident.1 = 'Patient_post_treatment',
                   ident.2 = 'Heathy_control',
                   logfc.threshold = 0.25)
DEG_T4_post_HC$gene <- rownames(DEG_T4_post_HC)
DEG_T4_post_HC$significance <- DEG_T4_post_HC$p_val_adj < 0.05 & abs(DEG_T4_post_HC$avg_log2FC) > 0.5
DEG_T4_post_HC <- DEG_T4_post_HC %>% filter(p_val_adj < 0.05)
saveRDS(DEG_T4_post_HC, file = "DEG_T4_post_HC.rds")
DEG_T4_post_HC <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/DEG_T4_post_HC.rds")

DEG_T4_post_pre <- FindMarkers(T_cells_CD4, 
                   ident.1 = 'Patient_post_treatment',
                   ident.2 = 'Patient_pre_treatment',
                   logfc.threshold = 0.25)
DEG_T4_post_pre$gene <- rownames(DEG_T4_post_pre)
DEG_T4_post_pre$significance <- DEG_T4_post_pre$p_val_adj < 0.05 & abs(DEG_T4_post_pre$avg_log2FC) > 0.5
DEG_T4_post_pre <- DEG_T4_post_pre %>% filter(p_val_adj < 0.05)
saveRDS(DEG_T4_post_pre, file = "DEG_T4_post_pre")
DEG_T4_post_pre <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/DEG_T4_post_pre.rds")

Idents(B_cells) <- 'Condition'
levels(B_cells)
DEG_B_pre_HC <- FindMarkers(B_cells, 
                   ident.1 = 'Patient_pre_treatment',
                   ident.2 = 'Heathy_control',
                   logfc.threshold = 0.25)
DEG_B_pre_HC$gene <- rownames(DEG_B_pre_HC)
DEG_B_pre_HC$significance <- DEG_B_pre_HC$p_val_adj < 0.05 & abs(DEG_B_pre_HC$avg_log2FC) > 0.5
DEG_B_pre_HC <- DEG_B_pre_HC %>% filter(p_val_adj < 0.05)
saveRDS(DEG_B_pre_HC, file = "DEG_B_pre_HC.rds")
DEG_patpost_HC <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/DEG_B_pre_HC.rds")

DEG_B_post_HC <- FindMarkers(B_cells, 
                   ident.1 = 'Patient_post_treatment',
                   ident.2 = 'Heathy_control',
                   logfc.threshold = 0.25)
DEG_B_post_HC$gene <- rownames(DEG_B_post_HC)
DEG_B_post_HC$significance <- DEG_B_post_HC$p_val_adj < 0.05 & abs(DEG_B_post_HC$avg_log2FC) > 0.5
DEG_B_post_HC <- DEG_B_post_HC %>% filter(p_val_adj < 0.05)
saveRDS(DEG_B_post_HC, file = "DEG_B_post_HC.rds")
DEG_B_post_HC <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/DDEG_B_post_HC.rds")

Idents(Monocytes) <- 'Condition'
levels(Monocytes)
DEG_Mono_pre_HC <- FindMarkers(Monocytes, 
                   ident.1 = 'Patient_pre_treatment',
                   ident.2 = 'Heathy_control',
                   logfc.threshold = 0.25)
DEG_Mono_pre_HC$gene <- rownames(DEG_Mono_pre_HC)
DEG_Mono_pre_HC$significance <- DEG_Mono_pre_HC$p_val_adj < 0.05 & abs(DEG_Mono_pre_HC$avg_log2FC) > 0.5
DEG_Mono_pre_HC <- DEG_Mono_pre_HC %>% filter(p_val_adj < 0.05)
DEG_Mono_pre_HC <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/DEG_Mono_pre_HC.rds")

DEG_Mono_post_HC <- FindMarkers(Monocytes, 
                   ident.1 = 'Patient_post_treatment',
                   ident.2 = 'Heathy_control',
                   logfc.threshold = 0.25)
DEG_Mono_post_HC$gene <- rownames(DEG_Mono_post_HC)
DEG_Mono_post_HC$significance <- DEG_Mono_post_HC$p_val_adj < 0.05 & abs(DEG_Mono_post_HC$avg_log2FC) > 0.5
DEG_Mono_post_HC <- DEG_Mono_post_HC %>% filter(p_val_adj < 0.05)
saveRDS(DEG_Mono_post_HC, file = "DEG_Mono_post_HC.rds")
DEG_Mono_post_HC <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/DEG_Mono_post_HC.rds")

DEG_Mono_post_pre <- FindMarkers(Monocytes, 
                   ident.1 = 'Patient_post_treatment',
                   ident.2 = 'Patient_pre_treatment',
                   logfc.threshold = 0.25)
DEG_Mono_post_pre$gene <- rownames(DEG_Mono_post_pre)
DEG_Mono_post_pre$significance <- DEG_Mono_post_pre$p_val_adj < 0.05 & abs(DEG_Mono_post_pre$avg_log2FC) > 0.5
DEG_Mono_post_pre <- DEG_Mono_post_pre %>% filter(p_val_adj < 0.05)
saveRDS(DEG_Mono_post_pre, file = "DEG_Mono_post_pre.rds")
DEG_Mono_post_pre <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/DEG_Mono_post_pre.rds")

```

#volcano plot

```{r, warning=FALSE, message=FALSE, eval=FALSE}
library(EnhancedVolcano)
EnhancedVolcano(DEG_B_pre_HC,
                lab = rownames(DEG_B_pre_HC),
                x = "avg_log2FC",
                y = "p_val_adj")
EnhancedVolcano(DEG_B_post_HC,
                lab = rownames(DEG_B_post_HC),
                x = "avg_log2FC",
                y = "p_val_adj")
EnhancedVolcano(DEG_T4_pre_HC,
                lab = rownames(DEG_T4_pre_HC),
                x = "avg_log2FC",
                y = "p_val_adj")
EnhancedVolcano(DEG_T4_post_HC,
                lab = rownames(DEG_T4_post_HC),
                x = "avg_log2FC",
                y = "p_val_adj")
EnhancedVolcano(DEG_Mono_pre_HC,
                lab = rownames(DEG_Mono_pre_HC),
                x = "avg_log2FC",
                y = "p_val_adj")
EnhancedVolcano(DEG_Mono_post_HC,
                lab = rownames(DEG_Mono_post_HC),
                x = "avg_log2FC",
                y = "p_val_adj")
EnhancedVolcano(DEG_Mono_post_pre,
                lab = rownames(DEG_Mono_post_pre),
                x = "avg_log2FC",
                y = "p_val_adj")                

```


#ego 有做篩選
#GO不能有篩選


#clusterProfiler Monocyte
```{r, warning=FALSE, message=FALSE, eval=FALSE}
#clusterProfiler Monocyte
saveRDS(gsea_Mono_pre_HC_BP, file = "gsea_Mono_pre_HC_BP.rds")
gsea_Mono_pre_HC_BP <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/gsea_Mono_pre_HC_BP.rds")
saveRDS(gsea_Mono_post_HC_BP, file = "gsea_Mono_post_HC_BP.rds")
gsea_Mono_post_HC_BP <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/gsea_Mono_post_HC_BP.rds")
saveRDS(gsea_Mono_post_pre_BP, file = "gsea_Mono_post_pre_BP.rds")
gsea_Mono_post_pre_BP <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/gsea_Mono_post_pre_BP.rds")

#Gene list (Dataframe)
Mono_pre_HC <- DEG_Mono_pre_HC %>%
  dplyr::filter(!is.na(avg_log2FC)) %>%
  dplyr::arrange(desc(avg_log2FC)) %>%
  dplyr::select(gene, avg_log2FC)

#Convert to GSEA input datatype(vector)
Mono_pre_HC_geneList <- Mono_pre_HC$avg_log2FC
names(Mono_pre_HC_geneList) <- Mono_pre_HC$gene
Mono_pre_HC_geneList <- sort(Mono_pre_HC_geneList, decreasing = TRUE)


gsea_Mono_pre_HC_BP <- gseGO(
  geneList     = Mono_pre_HC_geneList,
  OrgDb        = org.Hs.eg.db,
  keyType      = "SYMBOL",
  ont          = "BP",
  minGSSize    = 10,
  maxGSSize    = 500,
  pvalueCutoff = 0.05,
  verbose      = FALSE
)

Mono_pre_HC_BP <- gsea_Mono_pre_HC_BP@result
write.csv(Mono_pre_HC_BP, file = "Mono_pre_HC_BP.csv", row.names = FALSE)

dotplot(gsea_Mono_pre_HC_BP, showCategory=10, split=".sign") + facet_grid(.~.sign)

gseaplot2(
  gsea_Mono_pre_HC_BP,
  geneSetID = "GO:0060337",
  title = "GO:0060337 type I interferon-mediated signaling pathway"
)

gseaplot2(
  gsea_Mono_pre_HC_BP,
  geneSetID = "GO:0071357",
  title = "GO:0071357 cellular response to type I interferon"
)

gseaplot2(
  gsea_Mono_pre_HC_BP,
  geneSetID = "GO:0001906",
  title = "GO:0001906 cell killing"
)

gseaplot2(
  gsea_Mono_pre_HC_BP,
  geneSetID = "GO:0002474",
  title = "GO:0002474 antigen processing and presentation of peptide antigen via MHC class I"
)

gseaplot2(
  gsea_Mono_pre_HC_BP,
  geneSetID = "GO:0035455",
  title = "GO:0035455 response to interferon-alpha"
)

gseaplot2(
  gsea_Mono_pre_HC_BP,
  geneSetID = "GO:0035456",
  title = "GO:0035456 response to interferon-beta"
)

gseaplot2(
  gsea_Mono_pre_HC_BP,
  geneSetID = "GO:0002434",
  title = "GO:0002434 immune complex clearance"
)

gseaplot2(
  gsea_Mono_pre_HC_BP,
  geneSetID = "GO:0043277",
  title = "GO:0043277 apoptotic cell clearance"
)

#Gene list (Dataframe)
Mono_post_HC <- DEG_Mono_post_HC %>%
  dplyr::filter(!is.na(avg_log2FC)) %>%
  dplyr::arrange(desc(avg_log2FC)) %>%
  dplyr::select(gene, avg_log2FC)

#Convert to GSEA input datatype(vector)
Mono_post_HC_geneList <- Mono_post_HC$avg_log2FC
names(Mono_post_HC_geneList) <- Mono_post_HC$gene
Mono_post_HC_geneList <- sort(Mono_post_HC_geneList, decreasing = TRUE)


gsea_Mono_post_HC_BP <- gseGO(
  geneList     = Mono_post_HC_geneList,
  OrgDb        = org.Hs.eg.db,
  keyType      = "SYMBOL",
  ont          = "BP",
  minGSSize    = 10,
  maxGSSize    = 500,
  pvalueCutoff = 0.05,
  verbose      = FALSE
)

Mono_post_HC_BP <- gsea_Mono_post_HC_BP@result
write.csv(Mono_post_HC_BP, file = "Mono_post_HC_BP.csv", row.names = FALSE)

dotplot(gsea_Mono_post_HC_BP, showCategory=10, split=".sign") + facet_grid(.~.sign)

gseaplot2(
  gsea_Mono_post_HC_BP,
  geneSetID = "GO:0002474",
  title = "GO:0002474 antigen processing and presentation of peptide antigen via MHC class I"
)

gseaplot2(
  gsea_Mono_post_HC_BP,
  geneSetID = "GO:0015986",
  title = "GO:0015986 proton motive force-driven ATP synthesis"
)

gseaplot2(
  gsea_Mono_post_HC_BP,
  geneSetID = "GO:0035455",
  title = "GO:0035455 response to interferon-alpha"
)

gseaplot2(
  gsea_Mono_post_HC_BP,
  geneSetID = "GO:0002434",
  title = "GO:0002434 immune complex clearance"
)

gseaplot2(
  gsea_Mono_post_HC_BP,
  geneSetID = "GO:0043277",
  title = "GO:0043277 apoptotic cell clearance"
)

#Gene list (Dataframe)
Mono_post_pre <- DEG_Mono_post_pre %>%
  dplyr::filter(!is.na(avg_log2FC)) %>%
  dplyr::arrange(desc(avg_log2FC)) %>%
  dplyr::select(gene, avg_log2FC)

#Convert to GSEA input datatype(vector)
Mono_post_pre_geneList <- Mono_post_pre$avg_log2FC
names(Mono_post_pre_geneList) <- Mono_post_pre$gene
Mono_post_pre_geneList <- sort(Mono_post_pre_geneList, decreasing = TRUE)


gsea_Mono_post_pre_BP <- gseGO(
  geneList     = Mono_post_pre_geneList,
  OrgDb        = org.Hs.eg.db,
  keyType      = "SYMBOL",
  ont          = "BP",
  minGSSize    = 10,
  maxGSSize    = 500,
  pvalueCutoff = 0.05,
  verbose      = FALSE
)

Mono_post_pre_BP <- gsea_Mono_post_pre_BP@result
write.csv(Mono_post_pre_BP, file = "Mono_post_pre_BP.csv", row.names = FALSE)

dotplot(gsea_Mono_post_pre_BP, showCategory=10, split=".sign") + facet_grid(.~.sign)

gseaplot2(
  gsea_Mono_post_pre_BP,
  geneSetID = "GO:0002399",
  title = "GO:0002399 MHC class II protein complex assembly"
)
gseaplot2(
  gsea_Mono_post_pre_BP,
  geneSetID = "GO:0002495",
  title = "GO:0002495 antigen processing and presentation of peptide antigen via MHC class II"
)
gseaplot2(
  gsea_Mono_post_pre_BP,
  geneSetID = "GO:0031640",
  title = "GO:0031640 killing of cells of another organism"
)

gseaplot2(
  gsea_Mono_post_pre_BP,
  geneSetID = "GO:0019724",
  title = "GO:0019724 B cell mediated immunity"
)
gseaplot2(
  gsea_Mono_post_pre_BP,
  geneSetID = "GO:0060337",
  title = "GO:0060337 type I interferon-mediated signaling pathway"
)
gseaplot2(
  gsea_Mono_post_pre_BP,
  geneSetID = "GO:0071357",
  title = "GO:0071357 cellular response to type I interferon"
)
```




```{r, warning=FALSE, message=FALSE, eval=FALSE}

data.dir <- "./CellChat_analysis"
if (!dir.exists(data.dir)) dir.create(data.dir)
setwd(data.dir)
#save load

saveRDS(cellchat.list, file = "cellchat.list.rds")
cellchat.list <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/CellChat_analysis/cellchat.list.rds")
saveRDS(cellchat, file = "cellchat.rds")
cellchat <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/CellChat_analysis/cellchat.rds")


public_data_all <- readRDS("C:/Users/User/OneDrive/Desktop/交大專題/實作/RDS/public_data_all.rds")
DefaultAssay(public_data_all) <- "RNA"

# Only NormalizeData is needed for CellChat (uses log-normalized 'data' slot)
# FindVariableFeatures and ScaleData are NOT required for CellChat
public_data_all <- NormalizeData(public_data_all)

# Split Seurat object based on the "Condition" metadata column
seurat.list <- SplitObject(public_data_all, split.by = "Condition")
```

```{r, warning=FALSE, message=FALSE, eval=FALSE}
# 3. Convert each Seurat object into a CellChat object and run the full single-dataset pipeline separately

cellchat.list <- lapply(names(seurat.list), function(x) {
  seurat_obj <- seurat.list[[x]]
   
  # Extract RNA log-normalized expression data
data.input <- GetAssayData(seurat_obj, assay = "RNA", slot = "data")
  
  # Extract metadata (CellStates used for grouping)
  meta <- seurat_obj@meta.data
  
  # Create CellChat object
  cellchat <- createCellChat(object = data.input, meta = meta, group.by = "singleR_labels_m")
  
  # Assign CellChat database (human)
  cellchat@DB <- CellChatDB.human
  
  # Subset genes and interactions supported by the database
  cellchat <- subsetData(cellchat)
  
  # Identify overexpressed genes and ligand-receptor interactions
  cellchat <- identifyOverExpressedGenes(cellchat)
  cellchat <- identifyOverExpressedInteractions(cellchat)
  
  # Project data onto protein-protein interaction (PPI) network
  cellchat <- projectData(cellchat, PPI.human)
  
  # ---- Compute cell-cell communication network ----
  cellchat <- computeCommunProb(cellchat)                   # Compute communication probability
  cellchat <- filterCommunication(cellchat, min.cells = 10) # Filter low-abundance interactions
  cellchat <- computeCommunProbPathway(cellchat)            # Compute pathway-level probability
  cellchat <- aggregateNet(cellchat)                        # Aggregate into @net and @netP
  
  # Compute network centrality measures (per condition)
  cellchat <- netAnalysis_computeCentrality(cellchat)
  
  return(cellchat)
})

names(cellchat.list) <- names(seurat.list)

# ======================================
# 4. Merge all CellChat objects for comparative analysis
# ======================================
# Note: if reloading previously saved objects from an older CellChat version (<1.6.0),
# run updateCellChat() on each object before merging, e.g.:
# cellchat.list <- lapply(cellchat.list, updateCellChat)

cellchat <- mergeCellChat(cellchat.list, add.names = names(cellchat.list))
print(cellchat)  # Display merged CellChat object summary

# ======================================
# 5. Post-merge: joint manifold learning and network similarity
#    These MUST be run on the merged object, not on individual objects
# ======================================

# Functional similarity
cellchat <- computeNetSimilarityPairwise(cellchat, type = "functional")
cellchat <- netEmbedding(cellchat, type = "functional")
cellchat <- netClustering(cellchat, type = "functional")

# Structural similarity
cellchat <- computeNetSimilarityPairwise(cellchat, type = "structural")
cellchat <- netEmbedding(cellchat, type = "structural")
cellchat <- netClustering(cellchat, type = "structural")
```

#cellchatting
```{r, warning=FALSE, message=FALSE, eval=FALSE}
#total number of interactions and interaction strength
interact_num <- compareInteractions(cellchat, show.legend = F, group = c(1,2,3))
interact_str <- compareInteractions(cellchat, show.legend = F, group = c(1,2,3), measure = "weight")
interact_num + interact_str
#netVisual
par(mfrow = c(1,2), xpd=TRUE)
netVisual_diffInteraction(cellchat, weight.scale = T)
netVisual_diffInteraction(cellchat, weight.scale = T, measure = "weight")
#interact-heatmap
heat_num <- netVisual_heatmap(cellchat)
heat_str <- netVisual_heatmap(cellchat, measure = "weight")
heat_num + heat_str
#cellchatting
weight.max <- getMaxWeight(cellchat.list, attribute = c("idents","count"))
par(mfrow = c(1,3), xpd=TRUE)
for (i in 1:length(cellchat.list)) {
  netVisual_circle(cellchat.list[[i]]@net$count, weight.scale = T, label.edge= T, edge.weight.max = weight.max[2], edge.width.max = 12, title.name = paste0("Number of interactions - ", names(cellchat.list)[i]))
}
#gene enrich
gene_enrich_HC_pre <- rankNet(cellchat, mode = "comparison", comparison = c(1, 2), stacked = F, do.stat = TRUE)
gene_enrich_HC_post <- rankNet(cellchat, mode = "comparison", comparison = c(1, 3), stacked = F, do.stat = TRUE)
gene_enrich_pre_post <- rankNet(cellchat, mode = "comparison", comparison = c(2, 3), stacked = F, do.stat = TRUE)
gene_enrich_HC_pre + gene_enrich_HC_post+gene_enrich_pre_post

i = 1
#outgoing signal
pathway.union <- union(cellchat.list[[i]]@netP$pathways, cellchat.list[[i]]@netP$pathways)
outgoing_signal_HC = netAnalysis_signalingRole_heatmap(cellchat.list[[i]], pattern = "outgoing", signaling = pathway.union, title = names(cellchat.list)[i])
outgoing_signal_pre = netAnalysis_signalingRole_heatmap(cellchat.list[[i+1]], pattern = "outgoing", signaling = pathway.union, title = names(cellchat.list)[i+1])
outgoing_signal_post = netAnalysis_signalingRole_heatmap(cellchat.list[[i+2]], pattern = "outgoing", signaling = pathway.union, title = names(cellchat.list)[i+2])
par(mfrow = c(1,3), xpd=TRUE)
outgoing_signal_HC + outgoing_signal_pre + outgoing_signal_post
#incoming signal
incoming_signal_HC = netAnalysis_signalingRole_heatmap(cellchat.list[[i]], pattern = "incoming", signaling = pathway.union, title = names(cellchat.list)[i], color.heatmap = "GnBu")
incoming_signal_pre = netAnalysis_signalingRole_heatmap(cellchat.list[[i+1]], pattern = "incoming", signaling = pathway.union, title = names(cellchat.list)[i+1],  color.heatmap = "GnBu")
incoming_signal_post = netAnalysis_signalingRole_heatmap(cellchat.list[[i+2]], pattern = "incoming", signaling = pathway.union, title = names(cellchat.list)[i+2],  color.heatmap = "GnBu")
par(mfrow = c(1,3))
incoming_signal_HC + incoming_signal_pre + incoming_signal_post
#overall signal
overall_signal_HC = netAnalysis_signalingRole_heatmap(cellchat.list[[i]], pattern = "all", signaling = pathway.union, title = names(cellchat.list)[i], color.heatmap = "OrRd")
overall_signal_pre = netAnalysis_signalingRole_heatmap(cellchat.list[[i+1]], pattern = "all", signaling = pathway.union, title = names(cellchat.list)[i+1], color.heatmap = "OrRd")
overall_signal_post = netAnalysis_signalingRole_heatmap(cellchat.list[[i+2]], pattern = "all", signaling = pathway.union, title = names(cellchat.list)[i+2], color.heatmap = "OrRd")
draw(overall_signal_HC + overall_signal_pre + overall_signal_post, ht_gap = unit(0.5, "cm"))
#netVisual_bubble
netVisual_bubble(cellchat, sources.use = 2, targets.use = c(1:5),  comparison = c(1, 2), angle.x = 45)
netVisual_bubble(cellchat, sources.use = 2, targets.use = c(1:5),  comparison = c(1, 3), angle.x = 45)
netVisual_bubble(cellchat, sources.use = 2, targets.use = c(1:5),  comparison = c(2, 3), angle.x = 45)
# Chord diagram
par(mfrow = c(1,2), xpd=TRUE)
netVisual_chord_gene(cellchat.list[[1]], sources.use = 2, targets.use = c(1:5), slot.name = 'net', net = net.up, lab.cex = 0.8, small.gap = 3.5, title.name = paste0("Up-regulated signaling in ", names(cellchat.list)[1]))
netVisual_chord_gene(cellchat.list[[1]], sources.use = 2, targets.use = c(1:5), slot.name = 'net', net = net.down, lab.cex = 0.8, small.gap = 3.5, title.name = paste0("Down-regulated signaling in ", names(cellchat.list)[1]))
```

```{r, warning=FALSE, message=FALSE}
# define a positive dataset, i.e., the dataset with positive fold change against the other dataset
pos.dataset = "Patient_pre_treatment"
# define a char name used for storing the results of differential expression analysis
features.name = pos.dataset
# perform differential expression analysis
cellchat <- identifyOverExpressedGenes(cellchat, group.dataset = "datasets", pos.dataset = pos.dataset, features.name = features.name, only.pos = FALSE, thresh.pc = 0.1, thresh.fc = 0.1, thresh.p = 1)
#> Use the joint cell labels from the merged CellChat object
# map the results of differential expression analysis onto the inferred cell-cell communications to easily manage/subset the ligand-receptor pairs of interest
net <- netMappingDEG(cellchat, features.name = features.name)
# extract the ligand-receptor pairs with upregulated ligands in LS
net.up <- subsetCommunication(cellchat, net = net, datasets = "Patient_post_treatment",ligand.logFC = 0.2, receptor.logFC = NULL)
# extract the ligand-receptor pairs with upregulated ligands and upregulated recetptors in NL, i.e.,downregulated in LS
net.down <- subsetCommunication(cellchat, net = net, datasets = "Patient_post_treatment",ligand.logFC = -0.1, receptor.logFC = -0.1)
gene.up <- extractGeneSubsetFromPair(net.up, cellchat)
gene.down <- extractGeneSubsetFromPair(net.down, cellchat)

pairLR.use.up = net.up[, "interaction_name", drop = F]
up_regulate <- netVisual_bubble(cellchat, pairLR.use = pairLR.use.up, sources.use = 2, targets.use = c(1:5), comparison = c(2,3),  angle.x = 90, remove.isolate = T,title.name = paste0("Up-regulated signaling in ", names(cellchat.list)[3]))
#> Comparing communications on a merged object
pairLR.use.down = net.down[, "interaction_name", drop = F]
down_regulate <- netVisual_bubble(cellchat, pairLR.use = pairLR.use.down, sources.use = 2, targets.use = c(1:5), comparison = c(2,3),  angle.x = 90, remove.isolate = T,title.name = paste0("Down-regulated signaling in ", names(cellchat.list)[3]))
#> Comparing communications on a merged object
up_regulate + down_regulate

par(mfrow = c(1,2), xpd=TRUE)
netVisual_chord_gene(cellchat.list[[3]], sources.use = 2, targets.use = c(1:5), , slot.name = 'net', net = net.up, title.name = paste0("Up-regulated signaling in ", names(cellchat.list)[3]))
netVisual_chord_gene(cellchat.list[[3]], sources.use = 2, targets.use = c(1:5), , slot.name = 'net', net = net.down, title.name = paste0("Down-regulated signaling in ", names(cellchat.list)[3]))

pathways.show <- c("CD4") 
weight.max <- getMaxWeight(cellchat.list, slot.name = c("netP"), attribute = pathways.show) # control the edge weights across different datasets(找不到物件 'weight.all')
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(cellchat.list)) {
  netVisual_aggregate(object.list[[i]], signaling = pathways.show, layout = "circle", edge.weight.max = weight.max[1], edge.width.max = 10, signaling.name = paste(pathways.show, names(cellchat.list)[i]))
}

```





